\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-28 paper2015asml.tex
starting to write background

In this work, we take a first step towards the ultimate goal of generating robotic motions that are consistent, legible and predictable for human observers and co-workers. We start with a survey where human observers rate robot motion quality. We generated a range of trajectories across multiple environments with different planners. The motion planning problem we chose required a (simulated) robot to move its arm from a specified end-effector start position to a desired end-effector goal position. Movies of these trajectories from multiple viewpoints were then presented to human observers using an online survey tool. The users were asked to rate different attributes of the trajectories. We also computed a large set of features for each trajectory. The feature set was designed to be easily extensible across different types of robots and also captures the relationship between the trajectories and the environment. We use the feature set, coupled with machine learning techniques, to build a classifier that predicts the human rating for a given trajectory. The classifiers also help in identifying a set of features that are the most important in predicting human preferences for robot trajectories. The classifiers could also form the basis for a new {\em data-driven{ approach to motion planning.

@@

>>>>

In this work, we take a first step towards the ultimate goal of generating robotic arm motions in cluttered environments that are acceptable for human observers and co-workers. We start with a survey where human observers rate robot motion quality. We generated a range of trajectories across multiple environments with different planners. The motion planning problems we chose required a (simulated) robot to move its arm from a specified end-effector start position to a desired end-effector goal position. Movies of these trajectories from multiple viewpoints were then presented to human observers using an online survey tool. The users were asked to rate different attributes of the trajectories. We also computed a large set of features for each trajectory. The feature set was designed to be easily extensible across different types of robots and also captures the relationship between the trajectories and the environment. We use the feature set, coupled with machine learning techniques, to build a classifier that predicts the human rating for a given trajectory. The classifiers also help in identifying a set of features that are the most important in predicting human preferences for robot trajectories. The classifiers could also form the basis for a new {\em data-driven{ approach to motion planning.

@@

Robot motion study for industrial has been primarily influenced by the need to generate smooth jerk-free trajectories that minimize wear and tear of internal parts. In recent years, there has been more interest in the generation of motions for robots working in human environments, i.e. environments with clutter and people working next to the robots. Most attention, though, has been focused on generating {\em collision-free} motions. Examples include the use of randomized planners, trajectory optimization techniques and deterministic search-based techniques. Such approaches have also been modified to account for other types of constraints, e.g. dynamic constraints or process constraints arising from the task.

Human motions have been the subject of recent stufy with the intent of determining whether there are certain motor or locomotor invariants that best describe human manipulation or locomotion. Human motion has been observed to be stereo-typical~\cite{Atkeson:85}, i.e. learned motion patterns that are repeatedly used. This requires less planning of individual motions and contributes to making human motions more deterministic and predictable. Human motion has also been found to be optimized Nyga et. al.~\cite{Nyga:2011} studied the reaching motions of several subjects in table-setting situations.
